Predicting trends in the quality of state-of-the-art neural networks without access to training or testing data

### 2020-12-30 submission/NatCom_cv_models.tex
fix typo in table

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|p{1in}|c|c|c|c|c|c|}
\hline
 Series                      & \#                    & Metric         & $\langle\log\Vert\mathbf{W}\Vert_{F}\rangle$ & $\langle\log\Vert\mathbf{W}\Vert_{\infty}\rangle$ & $\hat{\alpha}$ & $\langle\log\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}\rangle$ \\
\hline
\multirow{3}{4em}{VGG}       & \multirow{3}{1em}{6}  & RMSE           & 0.56 & 0.53 & 0.48          & \textbf{0.42}  \\
                             &                       & $R^2$          &  XXX &  XXX &  XXX          &  XXX           \\
                             &                       & Kendall-$\tau$ &  XXX &  XXX &  XXX          &  XXX           \\
\hline
\multirow{3}{4em}{ResNet}    & \multirow{3}{1em}{5}  & 0.9            & 1.4  & \textbf{0.61} & 0.66           \\
                             &                       & $R^2$          &  XXX &  XXX &  XXX          &  XXX           \\
                             &                       & Kendall-$\tau$ &  XXX &  XXX &  XXX          &  XXX           \\
\hline
\multirow{3}{4em}{ResNet-1K} & \multirow{3}{1em}{19} & 2.4            & 3.6  & \textbf{1.8}  & 1.9            \\
                             &                       & $R^2$          &  XXX &  XXX &  XXX          &  XXX           \\
                             &                       & Kendall-$\tau$ &  XXX &  XXX &  XXX          &  XXX           \\
\hline
\multirow{3}{4em}{DenseNet}  & \multirow{3}{1em}{4}  & 0.3            & 0.26 & \textbf{0.16} & 0.21           \\
                             &                       & $R^2$          &  XXX &  XXX &  XXX          &  XXX           \\
                             &                       & Kendall-$\tau$ &  XXX &  XXX &  XXX          &  XXX           \\
\hline
\end{tabular}
\end{center}
\caption{Quality metrics 
         (RMSE, smaller is better; $R^2$, XXX is better; and Kendall-$\tau$ rank correlation, XXX is better)
         for reported Top1 test error for pretrained models in each architecture series.  
         Column \# refers to number of models.  
         VGG, ResNet, and DenseNet were pretrained on ImageNet.  
         ResNet-1K was pretrained on ImageNet-1K. 
}
\label{table:cv-models}
\end{table}

>>>>

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|p{1in}|c|c|c|c|c|c|}
\hline
 Series                      & \#                    & Metric         & $\langle\log\Vert\mathbf{W}\Vert_{F}\rangle$ & $\langle\log\Vert\mathbf{W}\Vert_{\infty}\rangle$ & $\hat{\alpha}$ & $\langle\log\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}\rangle$ \\
\hline
\multirow{3}{4em}{VGG}       & \multirow{3}{1em}{6}  & RMSE           & 0.56 & 0.53 & 0.48          & \textbf{0.42}  \\
                             &                       & $R^2$          &  XXX &  XXX &  XXX          &  XXX           \\
                             &                       & Kendall-$\tau$ &  XXX &  XXX &  XXX          &  XXX           \\
\hline
\multirow{3}{4em}{ResNet}    & \multirow{3}{1em}{5}  & RMSE           &  0.9 & 1.4  & \textbf{0.61} & 0.66           \\
                             &                       & $R^2$          &  XXX &  XXX &  XXX          &  XXX           \\
                             &                       & Kendall-$\tau$ &  XXX &  XXX &  XXX          &  XXX           \\
\hline
\multirow{3}{4em}{ResNet-1K} & \multirow{3}{1em}{19} & RMSE           &  2.4 & 3.6  & \textbf{1.8}  & 1.9            \\
                             &                       & $R^2$          &  XXX &  XXX &  XXX          &  XXX           \\
                             &                       & Kendall-$\tau$ &  XXX &  XXX &  XXX          &  XXX           \\
\hline
\multirow{3}{4em}{DenseNet}  & \multirow{3}{1em}{4}  & RMSE           &  0.3 & 0.26 & \textbf{0.16} & 0.21           \\
                             &                       & $R^2$          &  XXX &  XXX &  XXX          &  XXX           \\
                             &                       & Kendall-$\tau$ &  XXX &  XXX &  XXX          &  XXX           \\
\hline
\end{tabular}
\end{center}
\caption{Quality metrics 
         (RMSE, smaller is better; $R^2$, XXX is better; and Kendall-$\tau$ rank correlation, XXX is better)
         for reported Top1 test error for pretrained models in each architecture series.  
         Column \# refers to number of models.  
         VGG, ResNet, and DenseNet were pretrained on ImageNet.  
         ResNet-1K was pretrained on ImageNet-1K. 
}
\label{table:cv-models}
\end{table}
